### 2020-11-13 README.Rmd
rebuilt package to update datasets and documentation. Also re-did readme to include only small example

@@

We present an example analysis using data from two [ForestGEO](https://forestgeo.si.edu/) plots:

* [Michigan Big Woods](https://doi.org/10.7302/wx55-kt18) research plot data. For more information see [here](http://hdl.handle.net/2027.42/156251).
* [Smithsonian Conservation Biology Institute (SCBI) ForestGEO](https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/tree/master/tree_main_census) research plot data. For more information see [here](https://doi.org/10.1890/13-0010.1).

```{r}
library(tidyverse)
library(forestecology)
library(snakecase)
library(skimr)
library(sf)
library(sfheaders)
# devtools::install_github("rvalavi/blockCV")
library(blockCV)
library(tictoc)
library(yardstick)
library(viridis)
library(lubridate)

run_scbi <- FALSE
run_bw <- FALSE
small_example <- TRUE
```

### Load & preprocess data

The data for the Big Woods plot are included in the package. For SCBI, we load and preprocess the data corresponding to the two census reflecting the time period over which we consider growth in dbh. We load them into R as "tibble" data frames thereby ensuring a standardized input/output format that can be used across all `tidyverse` packages @tidyverse. Furthermore, we ensure that the different variables have the correct names, types (`dbl`, `data`, `factor`).

**Big Woods**:

```{r, eval = run_bw}
# Big Woods
# Read in census data from 2008 & 2014
data(bw_census_2008, bw_census_2014, bw_species)

# Append additional species data
bw_census_2008 <- bw_census_2008 %>%
  left_join(bw_species, by = "sp") %>%
  select(-c(genus, species, latin))

**SCBI**:

For SCBI we will look at just a 9 ha section of the plot to speed calculations.

```{r, eval = run_scbi}
# SCBI
scbi_2013 <- 
  "https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/raw/master/tree_main_census/data/census-csv-files/scbi.stem2.csv" %>% 
  read_csv() %>% 
  select(
    treeID, stemID, sp, quadrat, gx, gy, dbh, 
    date = ExactDate, codes, status
  ) %>%
  mutate(date = mdy(date)) %>%
  filter(gx < 300, gy > 300, gy < 600)

scbi_2018 <-
  "https://github.com/SCBI-ForestGEO/SCBI-ForestGEO-Data/raw/master/tree_main_census/data/census-csv-files/scbi.stem3.csv" %>% 
  read_csv() %>% 
  select(
    treeID, stemID, sp, quadrat, gx, gy, dbh, 
    date = ExactDate, codes, status
  ) %>% 
  mutate(dbh = as.numeric(dbh),
         date = mdy(date))  %>%
  filter(gx < 300, gy > 300, gy < 600)
```

### Compute growth

For each plot we combine the two census data frames into a single data frame  that now includes a numerical variable `growth` reflecting the average annual growth of dbh in cm. Furthermore, variables that (in theory) remain unchanged between censuses appear only once, such as `gx`, `gy`, species-related variables. Variables that should change between censuses are tagged with `1/2` indicating earlier/later, such as `dbh1/dbh2`, `codes1/codes2`.

The resulting data frames are named with some variation of `growth_df`.

**Big Woods**:

```{r, eval = run_bw}
# Big Woods
id <- "treeID"

# we need to filter out the re-sprouts
bw_census_2014 <- bw_census_2014 %>% 
  filter(!str_detect(codes, 'R'))

bw_growth_df <-
  # Merge both censuses and compute growth:
  compute_growth(bw_census_2008, bw_census_2014, id) %>%
  mutate(
    sp = to_any_case(sp),
    sp = as.factor(sp),
    species = sp,
    family = as.factor(family),
    trait_group = as.factor(trait_group)) %>%
  # drop stemID
  select(-stemID)

**SCBI**:

```{r, eval = run_scbi}
# SCBI
census_df1 <- scbi_2013 
census_df2 <- scbi_2018
id <- "stemID"

scbi_growth_df <- 
  # Merge both censuses and compute growth:
  compute_growth(census_df1, census_df2, id) %>%
  # Convert growth from cm to mm to make result comperable
  mutate(growth = growth/10,
             sp = as.factor(sp))

**Comparison**:

```{r, eval = run_scbi & run_bw}
# Both Big Woods & SCBI
growth_df <- bind_rows(
  bw_growth_df %>% st_drop_geometry %>% select(growth) %>% mutate(site = "bw"),
  scbi_growth_df %>% st_drop_geometry %>% select(growth) %>% mutate(site = "scbi")
)
ggplot(growth_df, aes(x = growth, y = ..density.., fill = site)) +
  geom_histogram(alpha = 0.5, position = "identity", binwidth = 0.05) +
  labs(x = "Average annual growth in dbh (cm per yr)") +
  coord_cartesian(xlim = c(-0.5, 1))
```

### Add spatial information

We now add spatial information to the `growth_df` data frame. Specifically:

1. In order to control for study region "edge effects" (cite Waller?), we need a function that adds "buffers" of trees. In our case, since our model of interspecific competition relies on a spatial definition of who is a "neighboring competitor" and certain explanatory variables such as biomass are cumulative, we need to ensure that all trees being modeled are not biased to have different neighbor structure, in particular the trees at the boundary of study regions.
1. Assign each tree to a "fold" for cross-validation purposes. Conventional cross-validation schemes assign observations to folds by resampling individual observations at random. However, underlying this scheme is an assumption that the observations are independent. In the case of forest census data, observations exhibit spatial autocorrelation, and thus this dependence must be incorporated in our resampling scheme @roberts2017 @pohjankukka2017. Packages that have implemented spatial cross-validation include @valavi2019

Thus, before we can incorporate the above information to `growth_df`, we need to define two constants.

```{r}
cv_fold_size <- 100
max_dist <- 7.5
```

The first, `cv_fold_size` is the length of the folds, each fold is a square. The next, `max_dist` is the maximum distance for a tree's competitive neighborhood. Trees within this distance of each other are assumed to compete while those farther than this distance apart do not. Both these values are in the same units as `gx` and `gz`, most often this will be meters.

<!--
DA comment: I am not sure about the below so I took it out. We don't assume that competitive interactions are inversely related to distance. We assume that competitive interactions are equivalent between distance 0 and 7.5, but than zero after that. Canham has the inversely related structure but we don't.

Following Tobler's first law of geography that "everything is related to everything else, but near things are more related than distant things." @tobler1970firstlawofgeo, we assume that the degree of spatial autocorrelation is inversely-related to distance. However, we further assume that once trees are more than `r max_dist` meters apart, this autocorrelation is negligeable. -->

Other studies have estimated the value of `max_dist`; we use an average of estimated values [@canham2004, @canham2006, @uriarte2004, @tatsumi2013].

#### Defining buffers

We use the function `add_buffer_variable` to identify which trees are inside of a buffer region of size `max_dist`. The user will need to specify a study region and convert to a `sf_polygon`.

**Example of buffer at work**:

```{r}
# Boundary polygon
square_boundary <- tibble(
  x = c(0,0,1,1),
  y = c(0,1,1,0)
) %>% 
  sf_polygon()

# "Trees" in polygon
trees_df <- tibble(
    x = runif(100),
    y = runif(100)
  ) %>%
  sf_point()

# Buffer polygon
trees_df <- trees_df %>%
  add_buffer_variable(direction = "in", size = 0.1, region = square_boundary)

ggplot() +
  geom_sf(data = trees_df, aes(col = buffer))

**Big Woods**:

```{r, eval = run_bw}
# Bigwoods
data(bw_study_region)

# Add buffer variable to data frame
bw_growth_df <- bw_growth_df %>%
  add_buffer_variable(direction = "in", size = max_dist, region = bw_study_region)

ggplot() +
  geom_sf(data = bw_growth_df, aes(col = buffer))

**SCBI**:

```{r, eval = run_scbi}
# SCBI
# Study region boundary polygon
scbi_study_region <- 
 #tibble(x = c(0,400,400,0,0), y = c(0,0,640,640,0)) %>% 
  tibble(x = c(0,300,300,0,0), y = c(300,300,600,600,3)) %>% 
  sf_polygon()

# Add buffer variable to data frame
scbi_growth_df <- scbi_growth_df %>%
  add_buffer_variable(direction = "in", size = max_dist, region = scbi_study_region)

ggplot() +
  geom_sf(data = scbi_growth_df, aes(col = buffer))
```

#### Defining spatial cross-validation folds

We use the [`blockCV`](https://github.com/rvalavi/blockCV) package to define the spatial grid, whose elements will act as the folds in our leave-one-out (by "one" we mean "one grid block") cross-validation scheme. The upshot here is we add `foldID` to `growth_df` which identifies which fold each individual is in, and the creation of a `cv_grid_sf` object which gives the geometry of the cross validation grid.

**Big Woods**:

```{r, eval = run_bw}
# Big Woods
set.seed(76)
bw_cv_grid <- spatialBlock(
  speciesData = bw_growth_df, theRange = cv_fold_size, verbose = FALSE,
  # Some guess work in figuring this out:
  k = 28, xOffset = 0.5, yOffset = 0
)

# Add foldID to data
bw_growth_df <- bw_growth_df %>% 
  mutate(
    foldID = bw_cv_grid$foldID
  )

# Visualize grid. Why does fold 19 repeat?
bw_cv_grid$plots +
  geom_sf(data = bw_growth_df %>% sample_frac(0.2), aes(col=factor(foldID)), size = 0.1)

bw_growth_df <- bw_growth_df %>%
  filter(!foldID %in% c(19, 23, 21, 17, 8, 19)) %>%
  mutate(foldID = as.character(foldID))

# Deliverable
ggplot() +
  geom_sf(data = bw_growth_df, aes(col = foldID, alpha = buffer))

bw_cv_grid_sf <- bw_cv_grid$blocks %>%
  st_as_sf()
```

**SCBI**:

```{r, eval = run_scbi}
# SCBI
scbi_cv_grid <- spatialBlock(
  speciesData = scbi_growth_df, theRange = cv_fold_size, yOffset = 0.9999, k = 9, verbose = FALSE
)

# Add foldID to data
scbi_growth_df <- scbi_growth_df %>% 
  mutate(
    foldID = scbi_cv_grid$foldID
  )

# Visualize grid
scbi_cv_grid$plots +
  geom_sf(data = scbi_growth_df, aes(col=factor(foldID)), size = 0.1)

scbi_cv_grid_sf <- scbi_cv_grid$blocks %>%
  st_as_sf()
```

### Focal versus competitor trees

Next we create the `focal_vs_comp` data frame which connects each tree in `growth_df` to the trees in its competitive neighborhood range (as defined by `max_dist`). So for example, if `growth_df` consisted of two focal trees with two and three neighbors respectively, `focal_vs_comp` would consist of 5 rows.

This requires the `growth_df` data frame; `max_dist`, the scalar defining competitive range; `cv_grid_sf`, giving the cross validation grid; and the `id` variable as inputs.

```{r, eval = run_bw}
# Big Woods
if (!file.exists("focal_vs_comp_bw.Rdata")) {
  tic()
  focal_vs_comp_bw <- bw_growth_df %>% 
    create_focal_vs_comp(max_dist, cv_grid_sf = bw_cv_grid_sf, id = "treeID")
  toc()
  save(focal_vs_comp_bw, file = "focal_vs_comp_bw.Rdata")
} else {
  load("focal_vs_comp_bw.Rdata")
}
```

```{r, eval = run_bw}
# Big Woods
glimpse(focal_vs_comp_bw)
```

**SCBI**:

```{r, eval = run_scbi}
# SCBI
tic()
focal_vs_comp_scbi <- scbi_growth_df %>% 
  create_focal_vs_comp(max_dist, cv_grid_sf = scbi_cv_grid_sf, id = "stemID")
toc()
```

```{r, eval = run_scbi}
# SCBI
glimpse(focal_vs_comp_scbi)
```

### Model fit and prediction

**Big Woods**:

Now we are ready to fit the competition model with `fit_bayesian_model`. This function needs only the `focal_vs_comp` as an input. Other options allow the user to specify prior parameters and run a competitor-species identity shuffle (see below).

```{r, eval = run_bw}
# Big Woods
tic()
posterior_param_bw <- focal_vs_comp_bw %>% 
  fit_bayesian_model(prior_param = NULL, run_shuffle = FALSE)
toc()
```

This output has the posterior parameters for the specified competition model. This `posterior_param` output can be used to get predicted growths for each individual (with `predict_bayesain_model`) to test how well the model performs. Or this `posterior_param` output can be plotted (either the betas or lambdas with `plot_posterior_params`) to understand what controls growth and the nature of the competitive ineractions.

Here we calculate the RMSE

```{r, eval = run_bw}
# Big Woods
predictions <- focal_vs_comp_bw %>%
  predict_bayesian_model(posterior_param = posterior_param_bw) %>%
  right_join(bw_growth_df, by = c("focal_ID" = "treeID"))
predictions %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
```

Now we test whether the identity of the competitor matters. We do this by shuffling the identity of competitors (but not of focal trees or spatial locations or sizes) and fitting the model again. We then compare RMSEs to see whether competitor identity matters to competitive interactions.

```{r, eval = run_bw}
posterior_param_bw_shuffle <- focal_vs_comp_bw %>%
  fit_bayesian_model(prior_param = NULL, run_shuffle = TRUE)

# b) Make predictions and compute RMSE
predictions_shuffle <- focal_vs_comp_bw %>%
  predict_bayesian_model(posterior_param = posterior_param_bw_shuffle) %>%
  right_join(bw_growth_df, by = c("focal_ID" = "treeID"))
predictions_shuffle %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
```

The RMSE is lower for the non-shuffled version. This gives support for the idea that competitor identity does matter for competitive interactions.

**SCBI**:

```{r, eval = run_scbi}
# SCBI
tic()
posterior_param_scbi <- focal_vs_comp_scbi %>% 
  fit_bayesian_model(prior_param = NULL, run_shuffle = FALSE)
toc()
```

Here we provide examples of seeing how well the model fits and then a spatial plot of the residuals to see whether there are any consistent spatial patterns to them.

```{r, eval = run_scbi}
# SCBI
scbi_growth_df_noCV <- focal_vs_comp_scbi %>% 
  predict_bayesian_model(posterior_param = posterior_param_scbi) %>% 
  right_join(scbi_growth_df, by = c("focal_ID" = "stemID"))

scbi_growth_df_noCV %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)

# Observed vs predicted growth  
ggplot(scbi_growth_df_noCV, aes(x = growth, y = growth_hat)) +
  geom_point(size = 0.5, color = rgb(0, 0, 0, 0.25)) +
  stat_smooth(method = 'lm') +
  geom_abline(slope = 1, intercept = 0) +
  coord_fixed() + 
  labs(
    x = "Observed growth in dbh", y = "Predicted growth in dbh", 
    title = "Predicted vs Observed Growth"
  )

reslab <- expression(paste('Residual (cm ',y^{-1},')'))
scbi_growth_df_noCV %>% 
  st_as_sf() %>%
  # Need to investigate missingness
  filter(!is.na(growth_hat)) %>% 
  mutate(
    error = growth - growth_hat,
    error_bin = cut_number(error, n = 5), 
    error_compress = ifelse(error < -0.75, -0.75, ifelse(error > 0.75, 0.75, error))
  ) %>% 
  ggplot() + 
  geom_sf(aes(col = error_compress), size = 1) + 
  theme_bw() + 
  scale_color_gradient2(
    low = "#ef8a62", mid = "#f7f7f7", high = "#67a9cf", 
    name = reslab,
    breaks = seq(from = -0.75, to = 0.75, by = 0.25),
    labels = c('< -0.75', '-0.5', '0.25', '0', '0.25', '0.5', '> 0.75')) +
  labs(x = "Meter", y = "Meter")
```

### Run spatial cross-validation

For the above results we fit the model to the entire data set, and then make predictions across the entire data set from that fit. This could lead to overfitting because we are using the training data to also test the model. If model error is spatially correlated this could be a large issue (cite important sources here!). We can use the spatial block structure we defined above to deal with with. The function `run_cv` goes through each fold in the `cv_grid_sf` and fits the model on all the other folds. Then applies that fit to the focal fold. It is a wrapper for `fit_bayesain_model` and `predict_bayesain_model` but fits a separate model for each fold.

```{r, eval = run_bw}
# big woods
tic()
cv_bw <- focal_vs_comp_bw %>%
  run_cv(max_dist = max_dist, cv_grid = bw_cv_grid) %>%
  right_join(bw_growth_df, by = c("focal_ID" = "treeID"))
toc()

cv_bw %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
```

As expected this RMSE is higher than that when the model is fit without cross validation. See Allen and Kim (2020) for more discussion of this.

```{r, eval = run_scbi}
# SCBI
tic()
cv_scbi <- focal_vs_comp_scbi %>%
  run_cv(max_dist = max_dist, cv_grid = scbi_cv_grid) %>%
  right_join(scbi_growth_df, by = c("focal_ID" = "treeID"))
toc()

cv_scbi %>%
  rmse(truth = growth, estimate = growth_hat) %>%
  pull(.estimate)
```

Here also this RMSE is much higher than that for the above SCBI model fit without cross validation.

### Visualize posterior distributions

**Big Woods**

We might be interested in the posterior distributions of parameters. The betas tell us about how fast each species grows and how this depends on DBH. The lambdas, often of more interest, are the species-specific competition coefficients. The full lambda matrix gives competition strength between species. There is a rich literature on this matrix (cite).

Because of the structure of the `bw_fit_model` object we cannot simply draw these curves based on the posterior distribution. `bw_fit_model` gives the parameters *compared* to a baseline. This is not of direct interest. So to display these parameters, as we care about them, we have to sample from the baseline distribution and from the comparison one to get the posterior distribution of interest.

Here we re-run the Big Woods model but using the family as the group for comparison. This makes the posterior distributions easier to follow. Also, surprisingly, grouping by family performed just as well as grouping by species (see Allen and Kim 2020). First we re-run `create_focal_vs_comp` and `fit_bayesian_model` with the grouping variable as family.

```{r, eval = run_bw}

focal_vs_comp_bw <- bw_growth_df %>%
  # mutate(sp = trait_group) %>%
  mutate(sp = family) %>%
  create_focal_vs_comp(max_dist = max_dist, cv_grid_sf = bw_cv_grid_sf, id = "treeID")

# a) Fit model (compute posterior parameters) with no permutation shuffling
posterior_param_bw <- focal_vs_comp_bw %>%
  fit_bayesian_model(prior_param = NULL, run_shuffle = FALSE)

Now the output of `fit_bayesian_model` is passed to `plot_posterior_parameters`.

```{r, eval = run_bw}
# b) Recreate Fig5 from Allen (2020): Posterior distributions of selected lambdas
posterior_plots <- plot_posterior_parameters(
  posterior_param = posterior_param_bw,
  sp_to_plot = c("cornaceae", "fagaceae", "hamamelidaceae", "juglandaceae", "lauraceae", "rosaceae", "sapindaceae", "ulmaceae")
)
```

The output is a list with three plots stored. The element `beta_0` gives the growth intercept, i.e., how fast an individual of each group grows independent of DBH).

```{r, eval = run_bw}
posterior_plots[["beta_0"]]
```

Next `beta_dbh` gives the DBH-growth slope for each group.

```{r, eval = run_bw}
posterior_plots[["beta_dbh"]]
```

Finally `lambda` gives the competition coeffiencts.

```{r, eval = run_bw}
posterior_plots[["lambda"]]
```

**SCBI**

```{r, eval = run_scbi}
posterior_plots_scbi <- plot_posterior_parameters(
  posterior_param = posterior_param_scbi,
  sp_to_plot = c("quru", "litu", "cagl", "cato")
)
```

```{r, eval = run_scbi}
posterior_plots_scbi[["lambda"]]
```

### Using small example

Need to write this up for the readme.

```{r, eval = small_example}
# Read in census files
data(census_df1_ex, census_df2_ex)

@@

ex_growth_df <-
  # Merge both censuses and compute growth:
  compute_growth(census_df1_ex, census_df2_ex_no_r, id) %>%
  mutate(
    sp = to_any_case(sp),
    sp = as.factor(sp))

data("ex_study_region")

@@

ggplot() +
  geom_sf(data = ex_growth_df, aes(col = buffer), size = 2)

# Bert's solution: Manually create a blocks sf object
fold1 <- rbind(c(0, 0), c(5, 0), c(5, 5), c(0, 5), c(0, 0))
fold2 <- rbind(c(5, 0), c(10, 0), c(10, 5), c(5, 5), c(5, 0))
blocks <- bind_rows(
  sf_polygon(fold1),
  sf_polygon(fold2) ) %>%
  mutate(foldID = c(1, 2))

@@

ex_cv_grid_sf <- ex_cv_grid$blocks %>%
  st_as_sf()

# focal v comp
focal_vs_comp_ex <- ex_growth_df %>% 
  create_focal_vs_comp(max_dist, cv_grid_sf = ex_cv_grid_sf, id = "ID")

# fit the model
posterior_param_ex <- focal_vs_comp_ex %>% 
  fit_bayesian_model(prior_param = NULL, run_shuffle = FALSE)

@@

# plot posteriors
posterior_param_ex %>%
  plot_posterior_parameters()

# run model with CV
ex_bw <- focal_vs_comp_ex %>% 
  run_cv(max_dist = max_dist, cv_grid = ex_cv_grid) %>%
  right_join(ex_growth_df, by = c("focal_ID" = "ID"))

@@

>>>>

This package is designed to work for spaitally mapped, repeat censused forests plots. The package has commands to fit models of tree growth based on neighborhood competition. This can be used to estimate species-specific competition coefficients. The models can be fit with a spatial cross validation scheme to avoid overfitting. Additionally these models can test whether the idenity of competitors matters, by shuffling competitor identity and testing whether model preformance changes. See Allen and Kim (2020) for a full descripition.

@@

```{r}
library(tidyverse)
library(forestecology)
library(sf)
library(sfheaders)
library(blockCV)
library(yardstick)
```

Here we provide an example with a small dateset. First we combine the two census data files into a single `tibble` with the growth of each surviving individual.

```{r}
# Read in census files
data(census_df1_ex, census_df2_ex)

@@

ex_growth_df <-
  # Merge both censuses and compute growth:
  compute_growth(census_df1_ex, census_df2_ex_no_r, id) %>%
  mutate(
    sp = to_any_case(sp),
    sp = as.factor(sp)) 
```

All growth models in the package assume that two individuals compete if they are less than a specified distance away. Here we set this distance and put all individuals within this distance of a plot boundray in a buffer (since we do not have full information about their competitors).

```{r}
data("ex_study_region")

@@

ggplot() +
  geom_sf(data = ex_growth_df, aes(col = buffer), size = 2)
```

We then set blocks for the cross validation scheme.

```{r}
# Bert's solution: Manually create a blocks sf object
fold1 <- rbind(c(0, 0), c(5, 0), c(5, 5), c(0, 5), c(0, 0))
fold2 <- rbind(c(5, 0), c(10, 0), c(10, 5), c(5, 5), c(5, 0))
blocks <- bind_rows(
  sf_polygon(fold1),
  sf_polygon(fold2) ) %>%
  mutate(foldID = c(1, 2))

@@

ex_cv_grid_sf <- ex_cv_grid$blocks %>%
  st_as_sf()
```

We then create a `focal_v_comp` tibble which has a row for each competing pair of individuals (each pair of individuals within `max_dist` of one another).

```{r}

# focal v comp
focal_vs_comp_ex <- ex_growth_df %>% 
  create_focal_vs_comp(max_dist, cv_grid_sf = ex_cv_grid_sf, id = "ID")
```

With `focal_v_comp` we can then run the growth model and get predictions from it. Here we run the model without cross validation. Posterior estimates can be plotted to give, for example, the lambda matrix of competition coefficents.

```{r}
# fit the model
posterior_param_ex <- focal_vs_comp_ex %>% 
  fit_bayesian_model(prior_param = NULL, run_shuffle = FALSE)

@@

# plot posteriors
plot_ex <- posterior_param_ex %>%
  plot_posterior_parameters()

plot_ex[["lambda"]]

Here we repeat the model fitting but with cross-validation. Note the increase in RMSE.

```{r}
# run model with CV
ex_bw <- focal_vs_comp_ex %>% 
  run_cv(max_dist = max_dist, cv_grid = ex_cv_grid) %>%
  right_join(ex_growth_df, by = c("focal_ID" = "ID"))

@@

For fuller examples on actual datasets see ___.
